\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-02-16 paper/paper.tex
Fix future work

\subsubsection{IPv6 vs IPv4 phantom hosts}

@@

\paragraph{Website Fingerprinting}
Website Fingerprinting~\cite{wang2014effective,hayes2016k,sirinam2018deep} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to. WF uses a classifier to label the traffic as belonging to one of several known websites, or (in some variants), an unknown or background class. Though WF is commonly studied in the context of anonymous web browsing, a censor could also use WF to detect refraction networking by distinguishing known traffic patterns of legitimate uses of a decoy site from the traffic generated by refraction networking (unknown class). Alternatively, the censor could monitor all traffic for patterns consistent with a set of blocked websites.

@@

\scheme provides a much larger degree of engineering flexibility than previous
Refraction Networking schemes. Due to its modular design, different registration
protocols and applications can be used. One obvious direction is to further
study such alternatives. For instance, while we use a TapDance-like
registration, we could potentially cut down on the overhead of one-time
registration by using port-knocking or using a Telex-style~\cite{telex11} tag (in the Client
Hello rather than Application Data).

\paragraph{Client-side applications}
On the application side, \scheme provides an interesting opportunity to explore
\emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.
mask site), our application could connect back to a client after registration
from the phantom host address. Protocols like WebRTC mentioned in
Section~\ref{sec:webrtc} or other peer-to-peer protocols such as BitTorrent,
Skype, or Bitcoin.

\paragraph{Traffic Analysis}
\scheme could also support applications that tradeoff performance for
observability. While Slitheen offers ideal mimicry of decoys, it comes at a high
cost of overhead. \scheme mask site applications could implement Slitheen
in order to perfectly mimic the mask site's latency, packet timings, and payload
sizes. In addition, careful choice of mask sites may allow for higher
performance, as sites with more replaceable content can carry more covert data.

\paragraph{Long-term Deployment}
Ultimately, the goal for Refraction Networking protocols is to be useful in
circumventing censorship. While it has taken many years for research
protocols to mature, we are excited to see schemes like TapDance deployed in
practice~\cite{frolov2017isp}. We believe \scheme can be even easier to deploy
at scale, and hope to leverage the existing success of TapDance to place \scheme
stations in real-world ISPs.

>>>>

\subsubsection{IPv6 vs.\ IPv4 Phantom Hosts}

@@

\paragraph{Website fingerprinting}
Website Fingerprinting~\cite{wang2014effective,hayes2016k,sirinam2018deep} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to. WF uses a classifier to label the traffic as belonging to one of several known websites, or (in some variants), an unknown or background class. Though WF is commonly studied in the context of anonymous web browsing, a censor could also use WF to detect refraction networking by distinguishing known traffic patterns of legitimate uses of a decoy site from the traffic generated by refraction networking (unknown class). Alternatively, the censor could monitor all traffic for patterns consistent with a set of blocked websites.

@@

\scheme provides a much larger degree of engineering flexibility than previous
Refraction Networking schemes. Due to its modular design, different registration
protocols and applications can be used. One obvious direction is to further
study such alternatives. For instance, while we use a TapDance-like
covert channel for registration, we could potentially cut down on the overhead of one-time
registration by using port-knocking or using a Telex-style~\cite{telex11} tag (in the Client Hello rather than Application Data).

\paragraph{Client-side applications}
On the application side, \scheme provides an interesting opportunity to explore
\emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.,
a mask site), our application could connect back to a client after registration
from the phantom host address. Possible protocols could include WebRTC, mentioned in
Section~\ref{sec:webrtc}, or other peer-to-peer protocols such as BitTorrent,
Skype, or Bitcoin.

\paragraph{Traffic analysis}
\scheme could also support applications that tradeoff performance for
observability. While Slitheen offers ideal mimicry of decoys, it comes at a high
cost of overhead. \scheme mask site applications could implement Slitheen
in order to perfectly mimic the mask site's latency, packet timings, and payload
sizes. In addition, careful choice of mask sites may allow for higher
performance, as sites with more replaceable content can carry more covert data.

\paragraph{Long-term deployment}
Ultimately, the goal for Refraction Networking protocols is to be useful in
circumventing censorship. While it has taken many years for research
protocols to mature, we are excited to see schemes like TapDance deployed in
practice~\cite{frolov2017isp}. We believe \scheme can be even easier to deploy
at scale, and we hope to leverage the existing success of TapDance to place \scheme
stations at real ISPs.
